\documentclass[11pt,a4paper,paranthesis]{article}
\usepackage[top=1.2in, bottom=1.2in, left=1in, right=1in,includefoot]{geometry}
\usepackage{enumitem}
\usepackage{setspace} \usepackage{changepage}
\doublespacing
\usepackage[bottom]{footmisc} 
\usepackage[utf8]{inputenc} \usepackage{indentfirst}
\usepackage{graphicx, color}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{dcolumn, setspace}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{amsmath, amsfonts}
\usepackage{natbib, amssymb} \usepackage[breaklinks]{hyperref}
\usepackage{bbm, booktabs, array, ctable, longtable}
\usepackage{rotating}
\usepackage{footnote}
\bibliographystyle{apa}
\author{Marco Ceccarelli}
\title{ \large Calendar - To Do's}

\begin{document}
	\maketitle
\section{Team AW Tasks}
\begin{enumerate} [leftmargin=*]
	\item Referee report \\ 
	Due date: 10. January $\rightarrow$ first draft finished and sent out to AW on 05.Jan
	\item Proctoring CFI and correcting exams \\
	Due date: Finished 10. January
\end{enumerate}

\section{Project WR}
\subsection{Conference deadlines:}
\begin{enumerate}[leftmargin=1cm]
	\item EFA - deadline: February 1, 2018
	\item AFA - deadline:
	\item Swedish house of finance\footnote{\url{https://www.houseoffinance.se/invitation-call-papers-shof-misum-conference-sustainable-finance/}} - deadline: March 1, 2018
\end{enumerate}
\subsection{Writing}
\begin{enumerate} [leftmargin=*]
	\item Write up WR computation methodology
	\item Check Table Captions \\ Are they still relevant? What is it that you want to look and analyze in each of the tables? Are you getting at the issue in the right fashion?
\end{enumerate}

\subsection{Programming}
\begin{enumerate} [leftmargin=*]
	\item Change methodology in duration \\ 
	Account for the quarters that passed and not the number of observations!
	\item Download Compustat samples from the merged dataset s.t. the data will also include PERMNOs
	\item Merge 13F dataset with Bushee investor classification
	\item Merge 13F dataset with active share measure where available
	\item Make same analysis also for the S12 sample. What differences are there? Also, are there differences btw the S12 and the 13F? What if you look only at non-mutual fund 13Fs?
	\item Include firm level corporate governance and managerial skill measures. Construct a portfolio measure for both.
	\item Add cik-cusip mapping from Ekaterina Valkova table to potentially supplement the \#matches you have in the tax havens dataset
\end{enumerate}

\subsection{Going forward - Additional tests and analyses}
\begin{enumerate} [leftmargin=*]
	\item Portfolio construction on the basis of WR $\Rightarrow$ Does targeting firms with exploitative behaviour pay off?
\end{enumerate}
\bibliography{BibtexLibrary}
\end{document}
