\documentclass[11pt,a4paper,paranthesis]{article}
\usepackage[top=1.2in, bottom=1.2in, left=1in, right=1in,includefoot]{geometry}
\usepackage{enumitem}
\usepackage{setspace} \usepackage{changepage}
\doublespacing
\usepackage[bottom]{footmisc} 
\usepackage[utf8]{inputenc} \usepackage{indentfirst}
\usepackage{graphicx, color}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{dcolumn, setspace}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage[english]{babel}
\usepackage{amsmath, amsfonts}
\usepackage{natbib, amssymb} \usepackage[breaklinks]{hyperref}
\usepackage{bbm, booktabs, array, ctable, longtable}
\usepackage{rotating}
\usepackage{footnote}
\bibliographystyle{apa}
\author{Marco Ceccarelli}
\title{ \large Readings Summary}

\begin{document}
	\maketitle
	\tableofcontents

\section{Reading Notes - Project WR}

\subsection{Journal/article}
\begin{enumerate}
	\item ...
\end{enumerate}

\subsection{xxx}
\begin{enumerate}
	\item ...
\end{enumerate}

\subsection{xxx}
\begin{enumerate}
	\item ...
\end{enumerate}

\subsection{xxx}
\begin{enumerate}
	\item ...
\end{enumerate}

\subsection{xxx}
\begin{enumerate}
	\item ...
\end{enumerate}

\section{Reading Notes - Others}
\subsection{Programming guide and best practices}
\begin{enumerate}[leftmargin=*]
	\item[Automation] $\odot$ Automate everything that can be automated
	\item[.bat] $\odot$ Write a \textbf{batch file} that executes everything from beginning to end \& produces the final results of the analysis. You want to include everything from the data cleaning process to the regressions and output generation. \\
	$\odot$ It is best practice to \textbf{start the batch file by clearing contents from /temp and /output} folders, s.t. you make sure that the output is produced by the current code.
	\item[VerContr] $\odot$ Use a version control software! Git or BitBucket are 2 examples. Documentation for both can be be found at \url{https://software-carpentry.org/lessons/}
	\item[Directory] $\odot$ Make a structure of folders for each project, e.g. ...WR/build/ for the dataset compilation and ...WR/analysis/ for producing the final tables. \\
	$\odot$ In both folders you can include directories for \textbf{input, code, output, \& temp}. Make sure that you erase the contents from temp at the end of the batch file!\\
	$\odot$ The main idea behind directories is to have them organised according to \textbf{functionality} of scripts and data.
	\item[Keys] $\odot$ 
\end{enumerate}

\newpage
\subsection{Referee Report - It pays to partner with a firm that writes annual reports well}
\noindent \textbf{Stand of literature:}
\begin{itemize} [leftmargin=*]
	\item Firms with more opaque financial statements trade at a discount \citep{Hwang.2017}
	\item Firms most likely to have managed earnings have more complex financial statements \citep{Lo.2017}
	\item Firms with more opaque financial statements face more stringent borrowing conditions \citep{Ertugrul.2017}
\end{itemize}

\noindent \textbf{Motivation.} Why are strategic alliances a good setting to investigate the effects of partners' readability? 
\begin{enumerate} [leftmargin=*]
	\item Small amount of due diligence in entering strategic alliances, since these are considered standard contracts
	\item Importance [for investors] of indicators of success. Alliances have a small probability of success, but when successful, they generate a lot of value
	\item Pro forma announcements force investors to consult partners 10-Ks
\end{enumerate}

\noindent \textbf{Hypotheses development/ Mechanisms}
\begin{enumerate}[leftmargin=*]
	\item Investors find it hard to process complex financial statements. This holds also for professionals.
	\item Investors trust less readable 10Ks less \& consider the managers that wrote them less trustworthy \\
	$\Rightarrow$ This is founded in the psychology literature and the business literature. \cite{RENNEKAMP.2012} finds that more readable disclosures lead to stronger reactions from small investors, in an experimental scenario.
	\item Opaque 10Ks imply that investors cannot properly understand the ``fit'' of the partners. Investors will thus become cautious and underestimate the chances of success \\ {\color{red} What is the backing for this?}
	\item When investors consider partners untrustworthy, they will deem the alliance risky on a relational (opportunistic behaviour), operational (disrespect promised deal), compliance risk
	\item As the outcome of the alliance becomes riskier, prospect theory predicts a more poignant overweighting of losses, causing a more pessimistic view. Thus, investors will be more likely to sell the partners after the announcement.
\end{enumerate}

\bibliography{BibtexLibrary}
\end{document}
